---
title: "03_pilot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
source("helpers.R")
library(languageR)
library(lmerTest)
library(wesanderson)
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

Set the background to be white instead of gray.
```{r echo=FALSE, message=FALSE, warning=FALSE}
theme_set(theme_minimal())
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
d <- read.csv("../../data/03_pilot/03_pilot-merged.csv")
summary(d)
View(d)
```

Exclude participants based on first language:
```{r echo=FALSE, message=FALSE, warning=FALSE}
lang_exclude = d %>%
  select(workerid, subject_information.language) %>%
  filter(str_detect(subject_information.language,regex("english", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(subject_information.language,regex("englishg", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(subject_information.language,regex("engligh", ignore_case=TRUE),negate=TRUE)) %>%
  select(workerid, subject_information.language)
d_english_1 = d[!(d$workerid %in% lang_exclude$workerid),]
View(d_english_1)
```

Exclude participants based on browser:
```{r echo=FALSE, message=FALSE, warning=FALSE}
browser_exclude = d_english_1 %>%
  select(workerid, system.Browser) %>%
  filter(str_detect(system.Browser,regex("safari", ignore_case=TRUE),negate=TRUE)) %>%
  select(workerid, system.Browser)
d_browser_2 = d_english_1[(d_english_1$workerid %in% browser_exclude$workerid),]
View(d_browser_2)
```

Exclude participants based on confusion:
```{r echo=FALSE, message=FALSE, warning=FALSE}
confusion_exclude = d_browser_2 %>%
  select(workerid, subject_information.asses) %>%
  filter(str_detect(subject_information.asses,regex("no", ignore_case=TRUE),negate=TRUE)) %>%
  select(workerid, subject_information.asses)
d_confusion_3 = d_browser_2[(d_browser_2$workerid %in% confusion_exclude$workerid),]
View(d_confusion_3)
```

Isolate only critical trials:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_crit_trials_4 = d_confusion_3 %>%
  filter(trial_type=="crit")
View(d_crit_trials_4)
```

Change 'maximum' and 'minimum' columns to 'numeric' from 'factor' data type:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_crit_trials_4$maximum <- as.character(d_crit_trials_4$maximum)
d_crit_trials_4$maximum <- as.numeric(d_crit_trials_4$maximum)

d_crit_trials_4$minimum <- as.character(d_crit_trials_4$minimum)
d_crit_trials_4$minimum <- as.numeric(d_crit_trials_4$minimum)
View(d_crit_trials_4)
```

Add new column: range widths (maximum minus minimum):
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_range_width_5 = d_crit_trials_4 %>%
  mutate(range.width = maximum - minimum)
View(d_range_width_5)
```

Exclude single trial where 'maximum' and 'minimum' were recorded as 'NA':
```{r echo=FALSE, message=FALSE, warning=FALSE}
number_error_exclude = d_range_width_5 %>%
  select(minimum, maximum) %>%
  filter(str_detect(maximum,regex("NA", ignore_case=TRUE),negate=TRUE)) %>%
  select(minimum, maximum)
d_range_width_5_1 = d_range_width_5[(d_range_width_5$minimum %in% number_error_exclude$minimum),]
View(d_range_width_5_1)
```

View results grouped by critical vs filler trials:
```{r echo=FALSE, message=FALSE, warning=FALSE}
character_type.dist = d_range_width_5_1 %>%
  group_by(character_type) %>% 
  summarize(avg_range = mean(range.width), CI.Low = ci.low(range.width), CI.High = ci.high(range.width)) %>%
  mutate(YMin = avg_range - CI.Low, YMax = avg_range + CI.High)
dodge = position_dodge(.90)
axis_order = c("nerd", "hippie")

ggplot(character_type.dist, aes(x=factor(character_type, levels = axis_order), y=avg_range, fill=character_type)) +
  geom_bar(stat="identity", position=dodge) +
  geom_errorbar(aes(ymin=YMin, ymax=YMax) ,position=dodge, width=.25) +
  scale_x_discrete(labels=c("nerd" = "Nerd Characters", "hippie" = "Hippie Characters")) +
  labs(x="Character Type", y="Average Range Width") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette)
```

View results grouped by high- vs low-stakes trials:
```{r echo=FALSE, message=FALSE, warning=FALSE}
stakes.dist = d_range_width_5_1 %>%
  group_by(stakes) %>% 
  summarize(avg_range = mean(range.width), CI.Low = ci.low(range.width), CI.High = ci.high(range.width)) %>%
  mutate(YMin = avg_range - CI.Low, YMax = avg_range + CI.High)
dodge = position_dodge(.90)
axis_order = c("low", "high")

ggplot(stakes.dist, aes(x=factor(stakes, levels = axis_order), y=avg_range, fill=stakes)) +
  geom_bar(stat="identity", position=dodge) +
  geom_errorbar(aes(ymin=YMin, ymax=YMax) ,position=dodge, width=.25) +
  scale_x_discrete(labels=c("low" = "Low Stakes", "high" = "High Stakes")) +
  labs(x="Stakes Condition", y="Average Range Width") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette)
```

The fixed-effects model, with interaction--range width:
```{r echo=FALSE, message=FALSE, warning=FALSE}
m_fixed_effects_inter_03pilot = glm(range.width ~ character_type * stakes, data=d_range_width_5_1)
summary(m_fixed_effects_inter_03pilot)
```

The 'more complex' (most most complex) mixed-effects model--with interactions--two experiments, range width:
```{r echo=FALSE, message=FALSE, warning=FALSE}
m_mixed_effects_complex_03pilot = glmer(range.width ~ character_type * stakes + (1+character_type|workerid) + (1+stakes|workerid) + (1|crit_trial_number) + (1|image1) + (1|image2) + (1+character_type|item) + (1|name1) + (1|name2) + (1|answerer.gender) + (1|questioner.gender) + (1|time) + (1|subject_information.gender), data=d_range_width_5_1)
summary(m_mixed_effects_complex_03pilot)
```